Leadership across cultures and contexts: an exploratory analysis

### 2020-05-06 leadership_across_cultures_contexts.Rmd
Working on elasticnet model of high status

We then investigated if the proportion of text records with evidence for *High status* differed among the different levels of group structure, subsistence strategies, continental regions, and leader sex (again using a logistic mixed effects model with these variables as fixed effects and authors nested within cultures as random intercepts). There were modest differences. Hunter-gatherers and pastoralists were more likely to provide evidence for high status leaders, as was South America and East Asia. Female leaders were also more likely to be identified as high status. Somewhat counter-intuitively, the proportion of text records indicating high status leaders was lowest at the highest level of political organization, perhaps because it would have been superfluous to note that kings and chiefs were high status. See Figure \@ref(fig:groupstatus). For the table of coefficients, see Supplementary Table X.

@@

```{r heatmapsubsis, fig.cap="Heatmap of relative estimated marginal means of the levels of evidence for each outcome variable by each subsistence strategy. Estimated marginal means were standardized by rows, and therefore can only be compared within rows, i.e., the colors represent the relative amount of evidence across levels of the categorical predictor within the same outcome variable."}

plot(p_heatmap_subsis)
```

```{r heatmapregion, fig.cap="Heatmap of relative estimated marginal means of the levels of evidence for each outcome variable by each continental region. Estimated marginal means were standardized by rows. The colors therefore represent the relative amount of evidence within the same outcome variable."}

plot(p_heatmap_region)
```

```{r heatmapsex, fig.cap="Heatmap of relative estimated marginal means of the levels of evidence for each outcome variable by leader sex. Estimated marginal means were standardized by rows. The colors therefore represent the relative amount of evidence within the same outcome variable."}

plot(p_heatmap_sex)
```

```{r heatmapgroups, fig.cap="Heatmap of relative estimated marginal means of the levels of evidence for each outcome variable by each group context. Estimated marginal means were standardized by rows. The colors therefore represent the relative amount of evidence within the same outcome variable."}

plot(p_heatmap_groups)
```

>>>>

We then investigated if the proportion of text records with evidence for *High status* differed among the different levels of group structure, subsistence strategies, continental regions, and leader sex (again using a logistic mixed effects model with these variables as fixed effects and authors nested within cultures as random intercepts). There were modest differences. Hunter-gatherers and pastoralists were more likely to provide evidence for high status leaders, as were South America and East Eurasia. Female leaders were also more likely to be identified as high status. Somewhat counter-intuitively, the proportion of text records indicating high status leaders was lowest at the highest level of political organization, perhaps because it would have been superfluous to note that kings and chiefs were high status. See Figure \@ref(fig:groupstatus). For the table of coefficients, see Supplementary Table X.

@@

```{r heatmapsubsis, fig.width=10, fig.cap="Heatmap of relative estimated marginal means of the levels of evidence for each outcome variable by each subsistence strategy. Estimated marginal means were standardized by rows, and therefore can only be compared within rows, i.e., the colors represent the relative amount of evidence across levels of the categorical predictor within the same outcome variable."}

p_heatmap_subsis + theme_minimal(15)
```

```{r heatmapregion, fig.width=10, fig.cap="Heatmap of relative estimated marginal means of the levels of evidence for each outcome variable by each continental region. Estimated marginal means were standardized by rows. The colors therefore represent the relative amount of evidence within the same outcome variable."}

p_heatmap_region + theme_minimal(15)
```

```{r heatmapsex, fig.width=10, fig.cap="Heatmap of relative estimated marginal means of the levels of evidence for each outcome variable by leader sex. Estimated marginal means were standardized by rows. The colors therefore represent the relative amount of evidence within the same outcome variable."}

p_heatmap_sex + theme_minimal(15)
```

```{r heatmapgroups, fig.width=10, fig.cap="Heatmap of relative estimated marginal means of the levels of evidence for each outcome variable by each group context. Estimated marginal means were standardized by rows. The colors therefore represent the relative amount of evidence within the same outcome variable."}

p_heatmap_groups + theme_minimal(15)
```
